Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-13 GWLDCII.tex
a comment on a comment

\note{Following two paragraphs added to replace the sentence ``clearly $n-3 \not\in I_1^V$''}
We first show that $n-3 \not\in I_1^V$. In Case 1, the only way we could have $n-3 \in I_1^V$ is if $V$ admits some propagator $r$ with $I_1(r) = n-3$; from the figure, one end of $r$ would have to lie on edge $n-4$, and by Lemma~\ref{lem no fourth vertex} the other end would have to lie on edge $n-1$ or $n$. However, if $r = (n-4,n-1)$ then by [remark following cyclic intervals lemma] \hlfix{we would have $I_1^V(r) = n-4$}{because if it contributed $n-3$ it would never be able to contribute $n-4$?}, while if $r = (n-4,n)$ then $r$ is the clockwise-most propagator supported on vertex 1 and we would have $I_1^V(r) = 1$. Either way, we have $I_1^V(r) \neq n-3$.

>>>>

\note{Following two paragraphs added to replace the sentence ``clearly $n-3 \not\in I_1^V$''}\note{No, the argument is much simpler, by cyclic intervals $I_{1}^W(p) = n-3$, but $p$ is the last thing that can contribute at $n-3$, so for this to happen we must have $n-3\not\in I_1^V$.}
We first show that $n-3 \not\in I_1^V$. In Case 1, the only way we could have $n-3 \in I_1^V$ is if $V$ admits some propagator $r$ with $I_1(r) = n-3$; from the figure, one end of $r$ would have to lie on edge $n-4$, and by Lemma~\ref{lem no fourth vertex} the other end would have to lie on edge $n-1$ or $n$. However, if $r = (n-4,n-1)$ then by [remark following cyclic intervals lemma] \hlfix{we would have $I_1^V(r) = n-4$}{because if it contributed $n-3$ it would never be able to contribute $n-4$?}, while if $r = (n-4,n)$ then $r$ is the clockwise-most propagator supported on vertex 1 and we would have $I_1^V(r) = 1$. Either way, we have $I_1^V(r) \neq n-3$.
